Usage metrics

### 2020-12-14 inst/analysis/usage_metrics.Rmd
minor

jan <- FALSE

@@

base_dir <- params$base_dir
# Set the paths, and customize for Jan.
if (jan) {
  base_dir <- "/mnt/code/eval"
}
eval_calls_path <- paste0(base_dir, params$calls_packages_path)
corpus_path <- paste0(base_dir, params$corpus_path)
eval_static_path <- paste0(base_dir, params$static_evals_path)
```

@@

```{r read,echo=F,cache=F}
read_fst(eval_calls_path) %>% as_tibble() -> E_raw
read_fst(corpus_path) %>% as_tibble() -> C_raw

read_csv(eval_static_path) %>% semi_join(C_raw, by = "package") -> P
```

The two data sets are E and C for conciseness.  C is only used here to compute
the corpus size. E is used throughout. Recall that E_raw has the source data
with all columns. P corresponds to static information about the call sites.

```{r select-columns,echo=F}
E_raw %>% select(
  run_package = package, # The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, # Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, # Script file name (name of this run)
  ev_package = eval_source, # Package of the call site
  arg_size = expr_expression_length, # Size in bytes of eval argument string
  opcodes = direct_interpreter_eval # Non-recursive AST nodes traversed
) -> E # by the interpreter

@@

# Eval Calls Overiew
The corpus has `r corpus_size` packages, and the data set has 
`r nrow(E)` distinct calls to the `eval` and its variants.

```{r eval-calls-overview,echo=F}
nb_calls <- E %>%
  count(wt = duplicates) %>%
  .$n
eval_calls <- E %>%
  filter(ev_variant == "eval") %>%
  count(wt = duplicates) %>%
  .$n
evalq_calls <- E %>%
  filter(ev_variant == "evalq") %>%
  count(wt = duplicates) %>%
  .$n
eval.parent_calls <- E %>%
  filter(ev_variant == "eval.parent") %>%
  count(wt = duplicates) %>%
  .$n
local_calls <- E %>%
  filter(ev_variant == "local") %>%
  count(wt = duplicates) %>%
  .$n

@@

# Nb eval call sites

```{r nb-eval-call-sites, echo=F}
stopifnot(sum(is.na(E$src_ref)) == 0) # No NAs in scr_ref!

@@

```{r call-sites-violin-plot, echo=F}
E %>%
  group_by(ev_package) %>%
  mutate(sites = n_distinct(src_ref)) %>%
  ggplot(aes(x = ev_variant, y = sites, fill = ev_variant), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  # geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y = "Call sites per package") +
  theme(
    legend.position = c(0.5, 0.85),
    legend.box.background = element_rect(fill = "white", size = 0.1),
    legend.box = "horizontal",
    axis.title.x = element_blank()
  )

@@

```{r exercised-call-sites}
static_sites <- nrow(P)

@@

```{r amout-of-code}

@@

```{r amount_computations}
nb_events_in_eval <- E %>% summarise(nb_events = sum(opcodes))

@@

```{r nb-events-violin-plot}
E %>%
  filter(opcodes > 0) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Number of events in eval per package") +
  theme(legend.position = "none")

>>>>

jan <- TRUE

@@

base_dir <- params$base_dir
# Set the paths, and customize for Jan.
if (jan) {
  base_dir <- "/mnt/code/eval/run/package-evals-traced.9/"
}
eval_calls_path <- paste0(base_dir, params$calls_packages_path)
corpus_path <- paste0(base_dir, params$corpus_path)
eval_static_path <- paste0(base_dir, params$static_evals_path)
```

# Read

@@

```{r read,include=F}
read_fst(eval_calls_path) %>% as_tibble() -> E_raw
read_fst(corpus_path) %>% as_tibble() -> C_raw
read_csv(eval_static_path) %>% semi_join(C_raw, by = "package") -> P
```

The two data sets are `E` and `C` for conciseness.  `C` is only used here to 
compute the corpus size. `E` is used throughout. Recall that `E_raw` has the 
source data with all columns. `P` corresponds to static information about the
call sites.

```{r select-columns,echo=F}
E_raw %>% select(
  run_package = package, #      The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, #                       Script file name (name of this run)
  ev_package = eval_source, #   Package of the call site
  arg_size = expr_expression_length, # Size in bytes of eval argument string
  opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
) -> E #                               interpreter during eval (non-recursive).

@@

#  Variants

The corpus has `r corpus_size` packages, and the data set has `r nrow(E)` 
distinct calls to the `eval` and its variants. There are 
`r length(unique(E$ev_package))` corpus packages with `eval` calls (note that
we may not trigger all `eval`s in a package due to spotty covereage).

```{r variants,echo=F}
nb_calls <- E %>%
  count(wt = duplicates) %>%
  .$n
eval_calls <- E %>%
  filter(ev_variant == "eval") %>%
  count(wt = duplicates) %>%
  .$n
evalq_calls <- E %>%
  filter(ev_variant == "evalq") %>%
  count(wt = duplicates) %>%
  .$n
eval.parent_calls <- E %>%
  filter(ev_variant == "eval.parent") %>%
  count(wt = duplicates) %>%
  .$n
local_calls <- E %>%
  filter(ev_variant == "local") %>%
  count(wt = duplicates) %>%
  .$n

@@

# Triggered sites

```{r triggered-sites, include=F}
stopifnot(sum(is.na(E$src_ref)) == 0) # No NAs in scr_ref!

@@

```{r call-sites-violin-plot, include=F}
E %>%
  group_by(ev_package) %>%
  mutate(sites = n_distinct(src_ref)) %>%
  ggplot(aes(x = ev_variant, y = sites, fill = ev_variant), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  # geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y = "Call sites per package") +
  theme(
    legend.position = c(0.5, 0.85),
    legend.box.background = element_rect(fill = "white", size = 0.1),
    legend.box = "horizontal",
    axis.title.x = element_blank()
  ) -> PLOT

@@

```{r exercised-call-sites, include=F}
static_sites <- nrow(P)

@@

```{r amout-of-code, include=F}

@@

```{r amount_computations, include=F}
nb_events_in_eval <- E %>% summarise(nb_events = sum(opcodes))

@@

```{r nb-events-violin-plot,include=F}
E %>%
  filter(opcodes > 0) %>%
  ggplot(aes(x = "", y = opcodes, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Number of events in eval per package") +
  theme(legend.position = "none")
